Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-13 chapters/paper3.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues
updating plot for herschel buckley fit
Changes 1. Updated text in aim 2 and aim 3 chapters for better flow

It is also expected that the effective viscosity will be different between the four microstructures dependent upon the 
degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will be mimic 
shear banding in colloidal suspensions, resulting in a lowered effective viscosity compared to bijels without nematically 
ordered particles. \cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the 
interface will also yield insight into how the packing of the particles affects the rate at which particles will get 
ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest 
difference between initial and final particle order and lowest number of particles left on the interface once steady 
state has been established.

We begin our investigation by analyzing the domain size change over time for bijels stabilized by ellipsoidal particles. We also
focus our attention on the effect of the initial state of the particle monolayer, in addition to the addition or removal of magnetic
fields. We perform this analysis on bijels stabilized by oblate and prolate particles. Bijel templates simulated in Aim 1 with no
field and a field strength of $\bar{B} = 1$ stabilized with a particle volume fraction $\phi_p = 0.15$. We apply a field strength of
$\bar{B} = 1$ or switch off the applied field. This results in four setups, $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number, 
$Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where $\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent
spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the fluid and $\sigma$ is the surface tension
of the interface. We use five shear numbers, $Ca_s = 10^{-4}, 50^{-5}, 10{^-5}, 50^{-6}, 10^{-6}$.

\section{Results}\label{sec:results_p3}
\subsection{Microstructure change}

First we plot the domain size of each system over time to analyze the effect of application of shear and magnetic fields.

@@

From Figure \ref{fig:domain_size_time_shear}, domains generally coarsen with time but the presence of a magnetic field 
significantly alters the coarsening dynamics due to magnetic field driven particle reordering on the interface. In the 
$\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles,
This analysis highlights how the interplay between shear, capillary effects, and magnetic interactions governs bijel 
microstructural stability and evolution, offering insights into tunable bijel design for applications requiring controlled 
domain morphology. Domain coarsening

@@

Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
$\bar{B}: 0 \to 1$. We also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
cases. From the time evolution of the curvature, we show that the same mechanism drives domain coarsening in all cases. Domain
coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. Previous investigates have 
demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
\cite{gunther_timescales_2014} We focus our investigation on this aspect in the following section.

@@

Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
We probe these aspects of the particle monolayer in this section.

@@

From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
shear direction. Upon application of the magnetic field, the particle order to the direction of the magnetic field. When 
investigating the orientational ordering of a bijel simulated under a field strength of $\bar{B} = 1$, we see that there is
shear dependent decay of the orientational ordering when the magnetic field is removed. We also characterize similar behavior
when maintaining the applied field, indicating that two reasons for surface area reduction is present. These mechanisms are attributed
to reorientation of particles at the interface or ejection of particles from the interface. We can characterize the former mechanism
using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.

@@

From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
except for $\bar{B}: 0 \to 1$. Shear dependent $\langle \psi \rangle$ can be observed for some of the systems, indicating that the mechanism
of domain coarsening differs.The data for $\bar{B}: 0 \to 1$ is characterized as such due to a particle reorientation at the interface
in response to the field just after the magnetic field has been applied. To reduce the interfacial energy as the particles tilt from the 
interface, the interface moves with the particle until it jams in place. We can characterize the impact of the interfacial angle on the 
particle packing using the radial distribution function (rdf).

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/rdf-SS.png} 
    \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
    particles as a function of the applied shear rate at four different processing histories. We show that there are minor differences
    in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
    \label{fig:rdf_shear} 
\end{figure}

From Figure \ref{fig:rdf_shear}, we show that the change in the packing of the particles on the interface is not correlated to the change 
in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. We then characterize the proportion 
of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.

@@

We show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
sensitive to shear. Here we also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. This is consistent
with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
change. Next, we characterize how the microstructure and particle properties affect the constant rheology properties of the bijels.

The ordering of the particles play an important role in determining the rheology of suspensions as ordered particles can slip over one another
before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. We perform this analysis on the
structures we have simulated. First, we plot the shear stress over time.

Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained from the experiments performed. This is
attributed to the coarsening of the domains and reorientation of particles at the interface. To characterize the viscosity, we identify pseudo-steady
state regions within each of the shear stress plots and fit the stress identified within this pseudo-steady state region to the strain rate. We fit 
the stress to the strain using a Herschel-Buckley rheology model, $\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the experimental
shear stress, $\sigma_{y}$ is the yield stress of the bijel, $K$ is the flow consistency index and $n$ is the flow index.
Where appropriate, we include results corresponding to a shear capillary number of $Ca_s = 10^{-6}$.

From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{table:rheology_fit}. From Table 
\ref{table:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
of magnetic fields.

\begin{table}[h!]
    \centering
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.522 & 1.030 & $1.054 \cdot 10^{-4}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.570 & 0.975 & $5.365 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.629 & 0.886 & $4.238 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.714 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.569 & 0.984 & $5.803 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.604 & 0.923 & $5.496 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.618 & 0.909 & $7.161 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

% \begin{table}[h!]
%     \centering
%     \begin{tabular}{||c c c c c c c c c c c c c||} 
%      \hline
%      $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
%      \hline\hline
%      $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
%      \hline
%     \end{tabular}
%     \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
%     \label{table:model_params}
%     \end{table}

We characterize that the yield stress of bijels stabilized with oblate particles decrease as particle order increases while decreasing then increasing for 
prolate particles. This can be attributed to the morphology differences that lead to different interfacial packing, characterized with the rdf in Figure 
\ref{fig:rdf_shear}. We see that bijels stabilized with oblate particles do not pack as efficiently on the interface when a magnetic field is applied,
meaning that the interface can buckle more easily. In contrast prolate particles pack more densely which leads to the greater yield stress. The results
suggest that increasing the magnetic field onto bijels stabilized with prolate particles also causes the particle monolayer to more easily buckle 
upon application of shear.

>>>>

It is also expected that the effective viscosity will be different between the four microstructures dependent upon the 
degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will 
should resulting in a lowered effective viscosity compared to bijels without nematically 
ordered particles. \cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the 
interface will also yield insight into how the packing of the particles affects the rate at which particles will get 
ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest 
difference between initial and final particle order and lowest number of particles left on the interface once steady 
state has been established.

\section{Results}\label{sec:results_p3}

We begin our investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
Specifically, we investigate the effect that particle order has on the rheological response characterized. We are also interested in
identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, We apply a field strength of
$\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
$\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
fluid and $\sigma$ is the surface tension of the interface. We use five shear numbers, $Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.

The ordering of the particles play an important role in determining the rheology of suspensions as ordered particles can slip over one another
before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
We perform this analysis on the structures we have simulated. First, we plot the shear stress over time.

Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained in the simulations performed. This is
attributed to the coarsening of the domains and reorientation of particles at the interface. \cite{tavacoli_novel_2011,macmillan_rheological_2019} 
Tavacoli et al. investigated the rheological response of Ethanediol/Nitromethane bijels and identified that upon placement of a needle to calculate the yield
stress of the bijel, the structure of the material was irreversibly altered. \cite{tavacoli_novel_2011} Macmillian et al. identified that repeated 
shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
To characterize the viscosity, we identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
smallest for the longest duration. We fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
$\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
$K$ is the flow consistency index and $n$ is the flow index.Where appropriate, we include results corresponding to a shear capillary number of 
$Ca_s = 10^{-6}$ as in many stress responses, we show that $Ca_s = 10^{-6}$ may not always yield usable results.

From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{table:rheology_fit}. From Table 
\ref{table:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
of magnetic fields. From the Hershel Buckley fit, we also identified the flow index, consistency index and the yield stress of the bijels,
tabulated in Table \ref{table:rheology_fit}.

\begin{table}[h!]
    \centering
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.511 & 0.999 & $7.168 \cdot 10^{-5}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.579 & 0.944 & $4.008 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.642 & 0.888 & $4.945 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.715 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.561 & 0.965 & $4.618 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.597 & 0.899 & $5.025 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.606 & 0.885 & $6.435 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

We show in Table \ref{table:rheology_fit} that the application of magnetic fields makes the bijel rheological behavior more Newtonian for both particle 
morphologies. We also see that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices than bijel templates made with no
applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. We also characterize that the yield stress 
of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. The yield stress of 
bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We 
showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
In the following sections, we will investigate the magnetic field process and the effect of local particle ordering on the microstructure of the bijel.

\subsection{Microstructure change}

Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we have the additional parameter of an applied magnetic field and
ellipsoidal particles. In this section, we probe the effect of applied shear to the microstructure and particle properties of magnetically
responsive bijels stabilized by ellipsoidal particles. First we plot the domain size of each system over time to analyze the effect of application of 
shear and magnetic fields.

@@

From Figure \ref{fig:domain_size_time_shear}, domains coarsen with time in all cases. When increasing the applied magnetic field in the case of 
$\bar{B}:0 \rightarrow 1$, we see shear assisted domain coarsening characterized as a 20 \% and 10 \% increase in the domain size of bijels
stabilized by oblate and prolate particles respectively. This is approximately 5 times greater than the response observed in Figure \ref{fig:domain_size-field_on}
In the  $\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles.
To characterize whether the domain size coarsening observed arises from different phenomena in each case, the area averaged curvature is plotted.

@@

Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
$\bar{B}: 0 \to 1$. We also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
cases. From the time evolution of the curvature, we show that the same mechanism drives domain coarsening in all cases. Domain
coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. Previous investigations have 
demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
\cite{gunther_timescales_2014} We focus our investigation on this aspect in the following section.

@@

Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
We probe these aspects of the particle monolayer in this section. We plot the orientation of the particle to each cartesian axis 
to identify if we characterize shear induced ordering.

@@

From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
shear direction in the simulation time observed. Upon application of the magnetic field, the particle order to the direction of the magnetic field. 
When investigating the orientational ordering of a bijel simulated under a field strength of $\bar{B} = 1$, we see that there is
shear dependent decay of the orientational ordering when the magnetic field is removed. We also characterize similar behavior
when maintaining the applied field. The reorientation of particles in the $\bar{B}:1 \rightarrow 1$ indicates shear induced reorientation of the 
particles at the interface. From the curvature results characterized in Figure \ref{fig:gaussian_curvature_time_shear}, we saw that the coarsening is
shear independent. This indicates that the surface area of the interface decreases which can occur due to changes in the interfacial orientation of 
particles at the interface or a reduction in the number of particles at the interface. We can characterize the former mechanism
using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.

@@

From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
except for $\bar{B}: 0 \to 1$. Shear dependent $\langle \psi \rangle$ can be observed for some of the systems, indicating that the mechanism
of domain coarsening differs. The data for $\bar{B}: 0 \to 1$ is characterized as such due to a particle reorientation at the interface
in response to the field just after the magnetic field has been applied. To reduce the interfacial energy as the particles tilt from the 
interface, the interface moves with the particle until it jams in place. We then characterize the proportion 
of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.

% We can characterize the impact of the interfacial angle on the 
% particle packing using the radial distribution function (rdf).

% \begin{figure} 
%     \centering 
%     \includegraphics[scale=0.3]{../figures/results/paper3/rdf-SS.png} 
%     \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
%     particles as a function of the applied shear rate at four different processing histories. We show that there are minor differences
%     in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
%     \label{fig:rdf_shear} 
% \end{figure}

% From Figure \ref{fig:rdf_shear}, we show that the change in the packing of the particles on the interface is not correlated to the change 
% in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. We then characterize the proportion 
% of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.

@@

We show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
sensitive to shear. Here we also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. This is consistent
with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
change.
